Golf-Sport: Managing Operations \\ A Case Study in Optimization

### 2018-05-09 Paper.tex
Finalish
Final
Final code, final paper, submit away!

\begin{tabular}{ |c | c| }
\textbf{Variable} & \textbf{Description} \\
\textit{x} & Production/Sale of Product \textit{i} in Period \textit{j} \\
\textit{e} & Graphite Stock Carryover \\

@@

$$f(x) = \sum_{j=1}^{3}Rx_{i} - \sum_{j=1}^{3}Cx_{i} - \sum Ix_{i,3} $$

@@

	\item Increasing of minimum demand for items with currently a zero minimum

@@

Range sensitivity and resource increases were examined in regards to this problem.  The two main points of focus are a hypothetical increase in total maximum demand and proposed increases in advertising or graphite budget.  Both of these situations 

>>>>

\begin{tabular}{ |c | c| }
\hline
\textbf{Variable} & \textbf{Description} \\
\hline
\textit{x} & Production/Sale of Product \textit{i} in Period \textit{j} \\
\textit{e} & Graphite Stock Carryover \\
\hline
\end{tabular}
\vspace{5mm}

@@

$$f(x) = \sum{Rx_{i,j}} - \sum{Cx_{i,j}} - \sum Ix_{i,3} $$

@@

	\item Increasing of minimum demand for items with a current production minimum of zero

@@

Range sensitivity and resource increases were examined in regard to this problem.  The two main points of focus are a hypothetical increase in total maximum demand and proposed increases in advertising or graphite budget.  Both of these situations 
